### 2018-04-06 Manuscript/chapter4.tex
Virus p

>>>>

Viral infection was a comparatively minor problem in honeybees until the last century when Varroa destructor (an ectoparasitic mite) spread worldwide (\citealt{miteSpread}). This mite feeds on honeybee hemolymph (\citealt{hemolymph}), transmits cocktails of viruses, and supports replication of certain viruses (\citealt{miteVirus}, \citealt{miteVirus2}, \citealt{miteVirus3}). One of these viruses that has been linked to honeybee decline is Israeli Acute Paralysis Virus (IAPV). A positive-sense RNA virus of the Dicistroviridae family (\citealt{fam}), IAPV causes infected honeybees to display shivering wings, decreased locomotion, muscle spams, and paralysis, and 80\% of caged infected adult honeybees die prematurely (\citealt{symptoms}). IAPV has demonstrated higher infectious capacities than other honeybee viruses in certain conditions (\citealt{carrillo}) and is more prevalent in colonies that do not survive the winter (\citealt{winter}). Its role in the rising phenomenon of ``Colony Collapse Disorder'' (in which the majority of worker bees disappear from a hive) remains unclear: It has been implicated in some studies (\citealt{iapvCCD}, \citealt{iapvCCD2}) but not in other studies (\citealt{ccd1}, \citealt{iapvCCD3}, \citealt{fam}). Nonetheless, it seems likely that IAPV reduces colony strength and survival.
